Self Regulation Ontology Retest Analyses

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

```{r eval=FALSE}
#summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
summary(MCMCglmm(icc ~  task, random = ~dv, data=boot_df))
```

@@

summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
```

@@

```{r}
summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
```

```{r}
summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
```

@@

```{r}
boot_df %>%
  select(dv, p_time, task, pearson) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task),
            mean_pearson = mean(pearson))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  arrange(mean_pearson)

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```

>>>>

```{r eval=FALSE}
#summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
# m = MCMCglmm(icc ~  task, random = ~dv, data=boot_df, nitt = 1300, burnin = 300)
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_task_model.rds')
summary(m)
```

@@

# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
summary(m)
```

```{r}
# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
summary(m)
```

@@

```{r}
boot_df %>%
  select(dv, p_time, task, pearson) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task),
            mean_pearson = mean(pearson))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
```
